Manuscript

### 2015-05-02 inst/wtc-finland/manuscript2.Rmd
---

```{r initialize}
#library(devtools); install_github("statguy/Winter-Track-Counts")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)

@@

```{r figure-convolution-example}
r <- crop(study$studyArea$habitat, extent(3400000, 3410000, 7000000, 7010000))
plot(r)
forest <- calc(r, function(x) if (is.na(x) || x %in% c(0,45:255)) NA else x %in% 18:35)
plot(forest)
coords <- expand.grid(1:dim(r)[1], 1:dim(r)[2])
x <- smoothSubsets(r=forest, coords=coords, kernelFun=expKernel, scales=c(125, 1000), .parallel=T)
plot(flip(rasterFromXYZ(x[,c("x","y","value")]), direction="y"), asp=1)
```

>>>>

```{r initialize}
#library(devtools); install_github("statguy/Winter-Track-Counts")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)

@@

```{r figure-convolution-example}
r <- crop(study$studyArea$habitat, extent(3400000, 3410000, 7000000, 7010000))
#plot(r)
forest <- calc(r, function(x) if (is.na(x) || x %in% c(0,45:255)) NA else x %in% 18:35)
#plot(forest)
coords <- xyFromCell(r, cell=1:ncell(r))
#x0 <- smoothSubsets(r=forest, coords=coords[1:(400*10),], kernelFun=expKernel, scales=125, .parallel=F)
x <- smoothSubsets(r=forest, coords=coords, kernelFun=expKernel, scales=c(125, 1000), .parallel=T)
#plot(flip(rasterFromXYZ(x[,c("x","y","value")]), direction="y"), asp=1)
fileName <- study$context$getFileName(dir=study$context$processedDataDirectory, name="figure-b-1", region=study$studyArea$region)
save(x, file=fileName)
load(fileName)

r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
r1$value <- factor(r1$value, levels=0:255)
r2 <- as.data.frame(rasterToPoints(forest))
colnames(r2) <- c("x","y","value")
r2$value <- factor(r2$value, levels=0:1)

labelPanel <- function(p, text, x, y) {
  g <- tableGrob(data.frame(a=text), rows=NULL, cols=NULL, gpar.corefill=gpar(fill="white", col=NA))
  p + annotation_custom(grob=g, xmin=x, ymin=y, xmax=x, ymax=y)
}

gray <- gray.colors(2, start=0.2, end=0.8)
p1 <- ggplot(r1) + geom_raster(aes(x, y, fill=value)) + scale_fill_grey() + theme_raster() + labs(x=NULL, y=NULL) + scale_x_continuous(expand=c(0,0)) + scale_y_continuous(expand=c(0,0))
p2 <- ggplot(r2) + geom_raster(aes(x, y, fill=value)) + scale_fill_grey() + theme_raster() + labs(x=NULL, y=NULL) + scale_x_continuous(expand=c(0,0)) + scale_y_continuous(expand=c(0,0))
p3 <- ggplot(subset(x, scale==125)) + geom_raster(aes(x, y, fill=value)) + scale_fill_gradient(low=gray[1], high=gray[2]) + theme_raster() + labs(x=NULL, y=NULL) + scale_x_continuous(expand=c(0,0)) + scale_y_continuous(expand=c(0,0))
p4 <- ggplot(subset(x, scale==1000)) + geom_raster(aes(x, y, fill=value)) + scale_fill_gradient(low=gray[1], high=gray[2]) + theme_raster() + labs(x=NULL, y=NULL) + scale_x_continuous(expand=c(0,0)) + scale_y_continuous(expand=c(0,0))

p1 <- labelPanel(p1, "a)", min(r1$x), max(r1$y))
p2 <- labelPanel(p2, "b)", min(r1$x), max(r1$y))
p3 <- labelPanel(p3, "c)", min(r1$x), max(r1$y))
p4 <- labelPanel(p4, "d)", min(r1$x), max(r1$y))

p <- arrangeGrob(p1, p2, p3, p4, ncol=2)
saveFigure(p, "figure-b-1.png", width=17, height=17, dpi=200)

```
